Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2024-01-05 article.qmd
Rename Reaction to RateLaw

authors:
    -   name: Mauro Silberberg
        orcid: 0000-0002-2402-1100
        email: maurosilber@df.uba.ar
        affiliations:
        -   ref: UBA
        -   ref: CONICET
    -   name: Rahuman S. Malik-Sheriff
        orcid: 0000-0003-0705-9809
        email: sheriff@ebi.ac.uk
        affiliations:
        -   ref: EBI
    -   name: Henning Hermjakob
        orcid: 0000-0001-8479-0262
        email: hhe@ebi.ac.uk
        affiliations:
        -   ref: EBI
    -   name: Hernán E. Grecco
        corresponding: true
        orcid: 0000-0002-1165-4320
        email: hgrecco@df.uba.ar
        affiliations:
        -   ref: UBA
        -   ref: CONICET

>>>>

authors:
    -   name: Mauro Silberberg
        orcid: 0000-0002-2402-1100
        email: maurosilber@df.uba.ar
        affiliations:
        -   ref: UBA
        -   ref: CONICET
    -   name: Rahuman S. Malik-Sheriff
        orcid: 0000-0003-0705-9809
        email: sheriff@ebi.ac.uk
        affiliations:
        -   ref: EBI
    -   name: Hernán E. Grecco
        corresponding: true
        orcid: 0000-0002-1165-4320
        email: hgrecco@df.uba.ar
        affiliations:
        -   ref: UBA
        -   ref: CONICET
